Whittaker Models for Real Groups

### 2024-04-25 whittaker.tex
intermediate commit

@@

Another invariant of an irreducible $(\g, K)$-module~$\pi$ is the \emph{wave-front set} of $\pi$, written $\WF(\pi)$. It is the union of a (finite) set of nilpotent $G(\R)$ orbits in
$i\g(\R)^*=i\Hom_\R(\g(\R),\R)$. See \cite{howe_wave_front}, \cite{bv_local_structure}, \cite{HarrisHeOlafsson}.

@@

@@

\subsection{Actions of $Q_\sigma(G)$ on representations and invariants}

\subsubsection*{On representations} 
Since~$Q_\sigma(G)$ can be viewed as a group of automorphisms of~$G(\R)$,  it has a canonical action on equivalence classes of representations of~$G(\R)$, and therefore on~$(\g, K)$-modules. This action preserves  the property of being large\footnote{AA 15-II-2024: should say something about this using the fact that it comes from automorphisms, either here or in the section on large reps}. It also preserves $L$-packets by~\cite[Lemma 6.18]{Contragredient}, and acts transitively on an~$L$-packet\footnote{AA 01-IV-2023: this point was missing, and I think details should be included. I think the transitivity is easy using  the description of discrete series L-packets in the Congragredient paper in terms of Harish-Chandra parameters, plus the fact that every element of~$Q_{\sigma}(G)$ has a representative in the Weyl group of a given elliptic maximal torus. The point about the action preserving $L$-packets also follows from this, I think; and perhaps it gives a better argument for the preservation of $L$-packets than [Contragredient, Lemma 6.18], which looks better suited to the $\theta$-version.}.

>>>>

\subsubsection*{Representations}

We work mostly in the  algebraic setting of
$(\g,K)$-modules. However, mainly for the analytic wave front set
invariant we need to consider representations of $G(\R)$ on a Banach
space. Suppose $(\pi,V)$ is an irreducible representation of $G(\R)$ 
 where $V$ is a Banach space. The underlying
$(\g,K)$-module is on the space of $K$-finite vectors in
$V$. Conversely if $\pi$ is an irreducible $(\g,K)$-module it can be
realized as the $K$-finite vectors of some  Banach space
representation.

@@

Now suppose $(\pi,V)$ is an irreducible representation of $G(\R)$. 
See \cite{howe_wave_front}, \cite{bv_local_structure},
\cite{HarrisHeOlafsson} for the definition of the \emph{wave-front
  set} $\WF(\pi)$. This is an analytic invariant determined by the
singularities of the global character of $\pi$ near the identity. 
It is a closed $G(\R)$-invariant subset of the nilpotent cone in
$i\g(\R)^*$. As such it is the union of a finite number of nilpotent $G(\R)$-orbits.

@@

\begin{lemma}
There is a canonical isomorphism $\phi:Q_\sigma(G)\simeq Q_\theta(G)$ defined as follows.
Suppose $x\in Q_\sigma(G)=(\Gad)^\sigma/(G^\sigma)_\ad$.
We can choose a representative $g\in (\Gad)^\sigma$ of $x$ which is also in $(\Gad)^\theta$.
Define $\phi(x)$ to be the image of $g$ in $Q_\theta(G)=(\Gad)^\theta/(G^\theta)_\ad$.
This is independent of the choice of $g$ and $\phi$ is an isomorphism of pointed sets.
\end{lemma}

Based on the Lemma we define $Q(G)$ to be $Q_\sigma(G)$ or $Q_\theta(G)$, depending on the setting.

[This is an explicit version of the group cohomology argument. Some detail here...]

@@

\subsection{Action of $Q(G)$ on representations and invariants}

Since~$Q_\sigma(G)$ can be viewed as a group of automorphisms of~$G(\R)$,  it has a canonical action on equivalence classes of representations of~$G(\R)$, and therefore on~$(\g, K)$-modules. This action preserves  the property of being large\footnote{AA 15-II-2024: should say something about this using the fact that it comes from automorphisms, either here or in the section on large reps}. It also preserves $L$-packets by~\cite[Lemma 6.18]{Contragredient}, and acts transitively on an~$L$-packet\footnote{AA 01-IV-2023: this point was missing, and I think details should be included. I think the transitivity is easy using  the description of discrete series L-packets in the Congragredient paper in terms of Harish-Chandra parameters, plus the fact that every element of~$Q_{\sigma}(G)$ has a representative in the Weyl group of a given elliptic maximal torus. The point about the action preserving $L$-packets also follows from this, I think; and perhaps it gives a better argument for the preservation of $L$-packets than [Contragredient, Lemma 6.18], which looks better suited to the $\theta$-version.}.
